---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# COVID19dashboard

<!-- badges: start -->
[![R build status](https://github.com/etc5523-2020/r-package-assessment-YIWEN-JIANG-github/workflows/R-CMD-check/badge.svg)](https://github.com/etc5523-2020/r-package-assessment-YIWEN-JIANG-github/actions)
<!-- badges: end -->

## Overview

The goal of COVID19dashboard is to provides datasets and functions for run the COVID-19 shiny dashboard.

## Installation

The development version can be installed from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2020/r-package-assessment-YIWEN-JIANG-github")
```

## Get started

The data set records COVID-19 information since Dec 31, 2019 and provided by [Our World in Data](https://ourworldindata.org/coronavirus). 
The package include three data, which are `covid_raw`, `visitor_map` and `visitors_total`.  
- `covid_raw`: The data comes from covid_raw.rda. The data contains the COVID-19 information OF 210 countries since Dec 31, 2019.   
- `visitors_total`: The data comes from visitors_total.rda. The data contains the information how the number of visitors change sine pandemic for different places.   
- `visitor_map`:  The data comes from visitor_map.rda. The data added geometric information compare to `visitors_total`, it can be used to create map plot.    

By using the `launch_app()` function to run the shiny dashboard. The aim of this app is to complement the raw data by providing interactive visualisation, and used to compare the difference between the countries.  

```{r launch-shiny-app, eval=FALSE}
launch_app()
```

## Example

This is a basic example which shows you the COVID-19 data in this package:

```{r example}
library(COVID19dashboard)
library(tibble)
covid_raw
```

Change in the number of daily new cases in United States:

```{r usa-daily-new-cases}
library(ggplot2)
library(tidyverse)
covid_raw %>%
  dplyr::filter(location == "United States") %>%
  ggplot() +
  geom_line(aes(x = date, y = new_cases)) +
  theme_classic() +
  ylab("Number of Daily New Cases") +
  xlab("Date") +
  ggtitle("Number of Daily New Cases in United States")
```
